---
title: "R Notebook"
output: html_notebook
---

This is to demonstrate how to use 'eddyR' package to process EDDY run folder, an output of eddy-gpu program, and produce an interactive web resource to review the results.   This will generate all DDN graphs in JSON format, and summary_table.md.

One will need to install https://github.com/skimlab/eddyR to run this workflow.

Loading required library.
```{r}
library(eddyR)
```

Setting input and output folders.
```{r}
# a folder where EDDY outputs are stored -- *_EdgeList.txt
input_dir = "./eddy-runs/IPAH_B_cells_vs_Control_B_cells/"

# a folder where postprocessed summary results will be saved
output_dir = "./eddy-postproc/IPAH_B_cells_vs_Control_B_cells/summary"

# a folder where DDN files will be saved in JSON format
ddn_json_dir = "./eddy-postproc/IPAH_B_cells_vs_Control_B_cells/datasets/"
```

First, post process EDDY run to get DDNs, summary table and DDN graphs (if create_ddn_graph is set to TRUE). 
```{r}
eddy_postproc <- post_proc_EDDY_folder(eddy_run_dir = input_dir, create_ddn_graph = TRUE)
```

Write summary table in CSV format.
```{r, warning=FALSE}
write_eddy_postproc_to_csv(eddy_postproc, output_dir = output_dir)
```

Now, save DDN graphs into PDF files.
```{r, warning=FALSE}
write_eddy_postproc_DDN_to_pdf(eddy_postproc, output_dir = output_dir)
```

Then, save DDN graphs into JSON files.
```{r}
eddy_postproc <- write_eddy_postproc_DDN_to_json(eddy_postproc, json_dir = ddn_json_dir)
```

Finally, save summary table in Markdown format, which to be convereted to html later by pandoc or markdown converter.
```{r}
eddy_postproc <- write_eddy_summary_table_markdown(eddy_postproc, output_dir = output_dir)
```
